Precision calculations for cosmic shear

### 2017-02-07 limber2.tex
MK updated figure

@@

\paragraph{Kitching et al.~2016}

Eq.~\ref{eq:C_ell_full} is analogous to (7) and (8) from
\cite{2016arXiv161104954K} for a flat Universe and in the case of perfect
photometric redshifts, $p(z | z_{\rm p}) = \delta_{\rm D}(z - z_{\rm p})$, and
for a bin function that selects the redshift bin $i$, $W^{\rm SR}(z, z_{\rm p})
= 1_{z \in i-\mbox{th bin}}$. In \cite{2016arXiv161104954K} eq.~(7) is however the
factor $2/\pi$ missing.

In App.~A they derive the Limber approximation starting from the full spherical
projection. Note that their filter function $q$ defined in (31) has an
errornous factor of comoving distance $r$, and an additional factor $\pi/2$
appears.

Eq.~19 of \cite{2016arXiv161104954K} corresponds to our
(\ref{eq:P_ell_gamma}). \mk{Has to be checked.}

We can not reproduce the amplitude of the differences between the cases, neither for
the power spectrum nor for the shear correlation function (see Fig.~\ref{fig:xi_pm_K16}).

@@

  \begin{center}
    \resizebox{0.9\hsize}{!}{
      \includegraphics{figures/P_kappa_limber_delta_Rijt}
    }
  \end{center}

    \caption{Differences in percentage of spherical shear power spectra terms
    as function of wave mode $\ell$, see Table \ref{tab:cases}.
    The blue and red curves corresponds to the ones shown in Fig.~7.3 of \citet{vande2012}.
    }

>>>>

\mk{Not sure whether the following comments should be left in the draft.} One
notes that the difference between the full projection and second-order Limber
does not scale as expected with $\ell^{-4}$, but rather with $\ell^{-2}$. This
might be due to numercical noise that creates residual terms at the ${\cal
O}(\ell^{-2})$ which do not cancel. Also note that the numerical noise for
$\ell > 20$ is due to numerical integration errors for the full projection.

@@

\subsection{Kitching et al.~2016}

\cite{2016arXiv161104954K} compute the full projection of the weak-lensing power
spectrum, which they present as spherical-radial representation the 3D shear field.
Our results (\ref{eq:C_ell_full}) correspond to their equations (7) and (8)
for a flat Universe and in the case of perfect
photometric redshifts, $p(z | z_{\rm p}) = \delta_{\rm D}(z - z_{\rm p})$, and
for a bin function that selects the redshift bin $i$, $W^{\rm SR}(z, z_{\rm p})
= 1_{z \in i-\mbox{th bin}}$. In \cite{2016arXiv161104954K} eq.~(7) is however the
factor $2/\pi$ missing.

In App.~A \cite{2016arXiv161104954K} derives the spherical and extended
Limber approximation starting from the full spherical projection. Note that
their filter function $q$ defined in (31) has an errornous factor of comoving
distance $r$, and an additional factor $\pi/2$ appears. \mk{This is probably worded
too strongly.}

We can not reproduce the amplitude of the differences between the cases,
neither for the power spectrum nor for the shear correlation function (see
Figs.~\ref{fig:Cl_cases} and \ref{fig:xi_pm_K16}).

@@

  \begin{center}
    \resizebox{0.5\hsize}{!}{
      \includegraphics{figures/P_kappa_limber_delta_Rijt}
    }
  \end{center}

    \caption{Relative differences in percentage of spherical first- and second-order Limber
    shear power spectra with respect to the full projection
    as function of wave mode $\ell$, see Table \ref{tab:cases}. The redshift distribution
    and the cosmological parameters (see text) are chosen to match
    \citet{vande2012}, see their Fig.~7.3 for comparison.
    }
